\PaperTitle

### 2020-01-25 paper/filter_bubbles.tex
derp

We simulate over risk-aversion parameters $\gamma \in \{ 0, 0.3, 0.6, 1, 5 \}$, \ standard-deviation $\sigma \in \{ 0.25, 0.5, 1.0, 2.0, 4.0 \}$, correlation parameters $\rho\in \{ 0, 0.1, 0.3, 0.5, 0.7, 0.9 \} $ and degree of idiosyncrasy of individual valuations $\beta \in \{ 0, 0.4, 0.8, 1, 2, 5\}$. We argue that these parameters are representative. First, the values of $\gamma$ that we consider range from no risk aversion ($\gamma = 0$) to a very high risk aversion level under CARA preferences $(\gamma = 5)$. The correlation parameter, $\rho$, ranges from no correlation ($\rho = 0$) to nearly full correlation $(\rho = 0.9)$. $\beta$ ranges from the common value component playing no role $(\beta = 0)$ to the idiosyncratic component dominating the true valuations $(\beta = 5)$. Finally, the standard deviation ranges from little uncertainty $(\sigma = 0.25)$ to a large amount of uncertainty $(\sigma = 4)$. Thus, the range of considered parameter values cover the relevant portions of the parameter space in order to provide full insight into the behavior of the model. 
\par
When we consider results varying a single parameter, we group the results over the other parameters and provide reports varying only the parameter of interest. We report results for a relatively small consumption history $T=20$ with a product space size $N=200$. Unless otherwise reported, our results are robust to varying $N$.
\par

>>>>

We simulate over risk-aversion parameters $\gamma \in \{ 0, 0.3, 0.6, 1, 5 \}$, \ standard-deviation $\sigma \in \{ 0.25, 0.5, 1.0, 2.0, 4.0 \}$, correlation parameters $\rho\in \{ 0, 0.1, 0.3, 0.5, 0.7, 0.9 \} $ and degree of idiosyncrasy of individual valuations $\beta \in \{ 0, 0.4, 0.8, 1, 2, 5\}$. We argue that these parameters are representative. First, the values of $\gamma$ that we consider range from no risk aversion ($\gamma = 0$) to reasonably high risk aversion levels $(\gamma = 5)$. The correlation parameter, $\rho$, ranges from uncorrelated valuations ($\rho = 0$) to nearly fully correlated valuations $(\rho = 0.9)$. $\beta$ ranges from the common value component playing no role $(\beta = 0)$ to the idiosyncratic component dominating the true valuations $(\beta = 5)$. Finally, the standard deviation ranges from little uncertainty $(\sigma = 0.25)$ to a large amount of uncertainty $(\sigma = 4)$. Thus, the range of considered parameter values cover the relevant portions of the parameter space in order to provide full insight into the behavior of the model. 
\par
When we consider results varying a single parameter, we group the results over the other parameters and provide reports varying only the parameter of interest. We report results for a relatively small consumption history $T=20$ with a product space size $N=200$. Unless otherwise reported, our results are robust to varying $N$.
\par
